National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: A Bayesian integrated population model, demographic simulations and a Shiny interface show how

### 2023-02-10 analysis/paper/paper.Rmd
ongoing.

---
title: "Caribou Demographic Projection - interesting & informative title TBD"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Cheryl A Johnson
    email: cheryl-ann.johnson@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Anna M Calvert
    email: anna.calvert@ec.gc.ca
    institute: [ECCC]
    correspondence: false
institute:
  - ECCC: Environment and Climate Change Canada 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      number_sections: no
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: CaribouDemographicModel.bib
csl: "../templates/journal-of-forest-ecology-and-management.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: inline
---

@@

<!-- The actual document text starts here: -->

@@

knitr::kable(tbl,caption="Monitoring scenarios parameters and values (example values to stimulate discussion - what should these numbers be and why?)")
```

@@

```{r fig1, fig.cap="Anthropogenic disturbance and monitoring scenarios (examples to stimulate discussion).", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/distScnscmult3ay1aSf1.png"))

@@

>>>>

---
title: "National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: A Bayesian integrated population model, demographic simulations and a Shiny interface show how"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Cheryl A Johnson
    email: cheryl-ann.johnson@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Anna M Calvert
    email: anna.calvert@ec.gc.ca
    institute: [ECCC]
    correspondence: false
institute:
  - ECCC: Environment and Climate Change Canada 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      number_sections: no
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: CaribouDemographicModel.bib
csl: "../templates/journal-of-forest-ecology-and-management.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: inline
---

@@

<!-- The actual document text starts here: -->
# Abstract
Across fifty-eight boreal caribou ranges in Canada, both survival and recruitment decrease with the percentage of the range that is within five hundred metres of anthropogenic disturbance. However, there is also variation in demographic rates among ranges particularly where anthropogenic disturbance is low, and this variation leads to uncertainty in demographic projections derived from national disturbance-demographic relationships. Demographic projections derived from local range-specific demographic data are also uncertain because few places have enough long-term monitoring data to characterize local demographic-disturbance relationships. We present a simple Bayesian integrated population model to integrate prior information from national analysis of demographic-disturbance relationships with available local demographic data to reduce uncertainty in population viability projections. We combine this model with methods for simulating local population dynamics and monitoring to show how monitoring requirements depend on landscape condition. Where projected anthropogenic disturbance is very high or very low, reasonably accurate status projections can be made using only national demographic-disturbance relationships. Where uncertainty is higher, deploying few collars for more years may be a lower cost option for improving the reliability of status projections. We provide an R Shiny interface to enable others to explore the implications of alternative monitoring scenarios, disturbance trajectories, priors, and other model parameters for boreal caribou demographic projections.

@@

knitr::kable(tbl,caption="Monitoring scenarios parameters and values.")
```

@@

```{r fig1, fig.cap="Anthropogenic disturbance and monitoring scenarios.", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/distScnscmult3ay3aSf1.png"))

@@

```{r fig2, fig.cap="Power analysis example result.", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/powercmult3ay3aSf1.png"))
knitr::include_graphics(here::here("figs/forPaper/powerEffortcmult3ay3aSf1.png"))

#TO DO: figure out how to put no monitoring results on these graphs.
```
